---
title: "Faasm-NDP Mixed workload experimental results"
author: "Jakub Szewczyk"
date: "2022-01-28"
output:
  html_document:
    toc: yes
  pdf_document:
    toc: yes
params:
  input_path: "mixtable.csv"
---

```{r setup, include=FALSE}
library(tidyverse)
library(rio)
library(scales)
library(xtable)
knitr::opts_chunk$set(echo = FALSE)
```

```{r read_csv, include=FALSE}
# for interactive session:
# params <- list(input_path = "wtable.csv")

raw_csv <- import("mixtable.csv")

t_data <- raw_csv %>%
  mutate (
    opts_host = factor(opts_host),
    opts_user = factor(opts_user),
    opts_function = factor(opts_function),
    ndp_factor = factor(opts_ndp, levels = c(0, 0.25, 0.33, 0.50, 0.67, 0.75, 1.0, 2.0), labels = c("0%", "25%", "33%", "50%", "67%", "75%", "100%", "AoS")),
    ndp_percent = pmin(as.double(opts_ndp) * 100.0, 110.0),
    total_requests = (errors_count + results_count),
    error_rate = errors_count / (errors_count + results_count),
    # Work around bad outlier removal, use q3+1.5*IQR as an estimate of max non-outlier value
    latency_us_q99pct = pmin(latency_us_q99pct, latency_us_q3 + 1.5*(latency_us_q3 - latency_us_q1)),
    rps_offset = abs(avg_rps_avg_rps - opts_req_rps) / opts_req_rps
   )
function_name <- 'mixed0'

rps_accuracy <- if (min(t_data$avg_rps_avg_rps) < 1.0) 0.1 else 1

usms <- 1.0/1000.0
uss <- usms/1000.0

paper_plot_w <- 4
paper_plot_h <- 2.25
paper_font <- "serif"
paper_pointsize <- 10
paper_theme <- theme_minimal() +
  theme(
    plot.title=element_blank(),
    legend.margin=margin(0,0,0,0,"cm")
  )
set1_scale <- brewer_pal(palette="Set1")(24)
set1_scale[6] <- "#000000"
paper_disc_scale <- scale_color_manual(values = set1_scale)
paper_fill_scale <- scale_fill_manual(values = set1_scale)
paper_shape_scale <- scale_shape_manual(values = c(0,1,2,3,4,5,6,14))

paper_plot_path <- paste0('plots/', function_name, '_')
```

# Function = `r function_name`

## Latencies

### Latency median(rps)
```{r latency_rps_median}
# ymin = latency_us_q1*plot_scale, , ymax = latency_us_q3*plot_scale
gplt <- ggplot(t_data %>% filter(rps_offset < 0.05) %>% filter(opts_function == 'pcakmm'),
    aes(x = opts_first_rps, group = interaction(opts_first_ndp, opts_function), color = interaction(opts_first_ndp, opts_function))) +
  paper_disc_scale + paper_fill_scale + paper_shape_scale + paper_theme +
  geom_line(aes(y = latency_us_med*uss)) +
#  geom_point(aes(y = latency_us_med*uss, shape = ndp_factor)) +
  scale_x_log10(breaks = log_breaks(n=10), label = scales::label_comma(accuracy = rps_accuracy)) +
  scale_y_log10(breaks = c(0.01, 0.1, 0.25, 0.5, 1, 2, 4, 8, 16, 32), label = c('0.01', '0.1', '0.25', '0.5', '1', '2', '4', '8', '16', '32')) +
  labs(title = "Latency for a given request per second rate", color = "% NDP", shape = "% NDP") +
  xlab("Throughput [requests/second]") + ylab("Median latency [s]")

pdf(paste0(paper_plot_path, "latency_rps_median.pdf"), width=paper_plot_w, height=paper_plot_h, useDingbats = FALSE, family = paper_font, pointsize = paper_pointsize)
plot(gplt)
dev.off()
gplt
```

### Latency unloaded boxplot (rps = `r as.double((tibble(sort(t_data$opts_req_rps)) %>% distinct())[2,1])`)
```{r latency_rps_unloaded_boxplot}
gplt <- ggplot(t_data %>% filter(opts_req_rps == as.double((tibble(sort(t_data$opts_req_rps)) %>% distinct())[2,1])),
    aes(y = ndp_factor, color = ndp_factor)) +
  paper_disc_scale + paper_fill_scale + paper_shape_scale + paper_theme +
  geom_boxplot(stat="identity", aes(
    xmin = latency_us_q1pct*usms, xmax = usms*latency_us_q99pct,
    xlower = latency_us_q1*usms, xupper = latency_us_q3*usms,
    xmiddle = latency_us_med*usms)) +
  guides(color = "none") +
  ylab("% Offloaded") + xlab("Latency [ms]")

pdf(paste0(paper_plot_path, "latency_rps_unloaded_boxplot.pdf"), width=paper_plot_w, height=paper_plot_h*0.4, useDingbats = FALSE, family = paper_font, pointsize = paper_pointsize)
plot(gplt)
dev.off()

lat_table <- t_data %>% filter(opts_req_rps == as.double((tibble(sort(t_data$opts_req_rps)) %>% distinct())[2,1])) %>%
  select(ndp_factor,
    latency_us_q1pct, latency_us_q99pct,
    latency_us_q1, latency_us_q3,
    latency_us_med
  )
lat_table <- column_to_rownames(lat_table, var="ndp_factor")
print(file=paste0(paper_plot_path, "latency_rps_unloaded_table.tex"), xtable(lat_table),floating=FALSE,latex.environments=NULL,booktabs=TRUE)

gplt
```

Vertical:

```{r boxplot_v}
gplt <- ggplot(t_data %>% filter(opts_req_rps == as.double((tibble(sort(t_data$opts_req_rps)) %>% distinct())[2,1])),
    aes(x = ndp_factor, color = ndp_factor)) +
  paper_disc_scale + paper_fill_scale + paper_shape_scale + paper_theme +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  geom_boxplot(stat="identity", aes(
    ymin = latency_us_q1pct*usms, ymax = usms*latency_us_q99pct,
    lower = latency_us_q1*usms, upper = latency_us_q3*usms,
    middle = latency_us_med*usms)) +
  guides(color = "none") +
  xlab("% Offloaded") + ylab("Latency [ms]")

pdf(paste0(paper_plot_path, "latency_rps_unloaded_boxplot_v.pdf"), width=paper_plot_w*0.4, height=paper_plot_h, useDingbats = FALSE, family = paper_font, pointsize = paper_pointsize)
plot(gplt)
dev.off()
gplt
```

## Max RPS achieved

```{r max_rps}

max_rps_data <- t_data %>% group_by(opts_function, opts_first_ndp) %>% summarise(rps= max(avg_rps_avg_rps), first(ndp_factor))
gplt <- ggplot(max_rps_data,
    aes(x = opts_first_ndp, group = opts_function, color = opts_function)) +
  paper_disc_scale + paper_fill_scale + paper_shape_scale + paper_theme +
  geom_line(aes(y = rps)) +
  geom_point(aes(y = rps, shape = `first(ndp_factor)`)) +
  scale_x_continuous(breaks = c(0, 25, 33, 50, 67, 75, 100, 110), labels=(\(x) ifelse(x <= 100, as.character(x), 'AoS'))) +
  scale_y_continuous(breaks = breaks_pretty(n=10), label = scales::label_comma(accuracy = rps_accuracy), expand = c(0.1,0)) +
  labs(title = "Requests per second achieved", shape = "% NDP") +
  xlab("Fraction offloaded [%]") + ylab("Max throughput [req/second]")

pdf(paste0(paper_plot_path, "max_rps.pdf"), width=paper_plot_w, height=paper_plot_h, useDingbats = FALSE, family = paper_font, pointsize = paper_pointsize)
plot(gplt)
dev.off()
gplt
```

## Error rate

```{r plot_error_rate}
gplt <- ggplot(t_data, aes(x = opts_req_rps, y = error_rate * 100.0, group = ndp_factor, color = ndp_factor)) +
  geom_point(aes(shape = ndp_factor)) +
  geom_line() +
  paper_disc_scale + paper_fill_scale + paper_shape_scale + paper_theme +
  labs(title = "Error rate", color = "% NDP", shape = "% NDP") +
  ylab("Error %") + xlab("Requests/s")

pdf(paste0(paper_plot_path, "error_rate.pdf"), width=paper_plot_w, height=paper_plot_h, useDingbats = FALSE, family = paper_font, pointsize = paper_pointsize)
plot(gplt)
dev.off()
gplt
```

## Total bytes transferred over the network per request

```{r table_network}
net_table <- t_data %>%
  group_by(ndp_factor) %>%
  summarise(mean = mean((monitor_computenet_tx_bytes_sum + monitor_storagenet_tx_bytes_sum) / results_count))
net_table <- column_to_rownames(net_table, var="ndp_factor")
print(file=paste0(paper_plot_path, "network_table.tex"), xtable(net_table),floating=FALSE,latex.environments=NULL,booktabs=TRUE)

ggplot(t_data) +
  geom_line(stat = 'identity', aes(x = avg_rps_avg_rps, y = (monitor_computenet_tx_bytes_sum + monitor_storagenet_tx_bytes_sum) / results_count, group = ndp_factor, color = ndp_factor)) +
  paper_disc_scale + paper_fill_scale + paper_shape_scale + paper_theme +
  scale_x_continuous(trans = 'log', breaks = log_breaks(n=20), label = scales::label_comma(accuracy = 1), expand = c(0.01, 0.01)) +
  scale_y_continuous(trans = 'identity', breaks = breaks_pretty(n=10), label = scales::label_comma(accuracy = 1)) +
  labs(title = "Total bytes per request sent over network", color = "% NDP", shape = "% NDP") +
  xlab("Req/s") + ylab("bytes/request")
```

## CPU analysis

### Per-node System+User MS / Total MS
```{r cpums_load}
gplt <- ggplot(t_data %>% filter(rps_offset < 0.05, opts_function=='pcakmm'),
    aes(x = avg_rps_avg_rps, group = ndp_factor, color = ndp_factor)) +
  coord_cartesian(ylim = c(0, 100)) +
  paper_disc_scale + paper_fill_scale + paper_shape_scale + paper_theme +
  geom_line(aes(linetype="Compute", y = 100.0*(monitor_computecpums_user_sum + monitor_computecpums_nice_sum + monitor_computecpums_system_sum + monitor_computecpums_irq_sum + monitor_computecpums_softirq_sum)/(monitor_computecpums_user_sum + monitor_computecpums_nice_sum + monitor_computecpums_system_sum + monitor_computecpums_idle_sum + monitor_computecpums_iowait_sum + monitor_computecpums_irq_sum + monitor_computecpums_softirq_sum))) +
  geom_point(aes(shape=ndp_factor, y = 100.0*(monitor_computecpums_user_sum + monitor_computecpums_nice_sum + monitor_computecpums_system_sum + monitor_computecpums_irq_sum + monitor_computecpums_softirq_sum)/(monitor_computecpums_user_sum + monitor_computecpums_nice_sum + monitor_computecpums_system_sum + monitor_computecpums_idle_sum + monitor_computecpums_iowait_sum + monitor_computecpums_irq_sum + monitor_computecpums_softirq_sum))) +
  geom_line(aes(linetype="Storage", y = 100.0*(monitor_storagecpums_user_sum + monitor_storagecpums_nice_sum + monitor_storagecpums_system_sum + monitor_storagecpums_irq_sum + monitor_storagecpums_softirq_sum)/(monitor_storagecpums_user_sum + monitor_storagecpums_nice_sum + monitor_storagecpums_system_sum + monitor_storagecpums_idle_sum + monitor_storagecpums_iowait_sum + monitor_storagecpums_irq_sum + monitor_storagecpums_softirq_sum))) +
  geom_point(aes(shape=ndp_factor, y = 100.0*(monitor_storagecpums_user_sum + monitor_storagecpums_nice_sum + monitor_storagecpums_system_sum + monitor_storagecpums_irq_sum + monitor_storagecpums_softirq_sum)/(monitor_storagecpums_user_sum + monitor_storagecpums_nice_sum + monitor_storagecpums_system_sum + monitor_storagecpums_idle_sum + monitor_storagecpums_iowait_sum + monitor_storagecpums_irq_sum + monitor_storagecpums_softirq_sum))) +
  scale_x_log10(breaks = log_breaks(n=10), label = scales::label_comma(accuracy = 0.1)) +
  scale_y_continuous(breaks = breaks_pretty(n=10), label = scales::label_comma(accuracy = 1)) +
  labs(title = "CPU load", color = "% NDP", shape = "% NDP", linetype = "Node") +
  xlab("Throughput [requests/second]") + ylab("Node CPU utilization (%)")

pdf(paste0(paper_plot_path, "cpu_load.pdf"), width=paper_plot_w, height=paper_plot_h, useDingbats = FALSE, family = paper_font, pointsize = paper_pointsize)
plot(gplt)
dev.off()
gplt
```

### Cluster-total System+User MS / Total MS
```{r total_utilization}
gplt <- ggplot(t_data %>% filter(rps_offset < 0.05),
    aes(x = avg_rps_avg_rps, group = ndp_factor, color = ndp_factor)) +
  coord_cartesian(ylim = c(0, 100)) +
  paper_disc_scale + paper_fill_scale + paper_shape_scale + paper_theme +
  geom_line(aes(y = 100.0*(12.0/38.0)*(monitor_storagecpums_user_sum + monitor_storagecpums_nice_sum + monitor_storagecpums_system_sum + monitor_storagecpums_irq_sum + monitor_storagecpums_softirq_sum)/(monitor_storagecpums_user_sum + monitor_storagecpums_nice_sum + monitor_storagecpums_system_sum + monitor_storagecpums_idle_sum + monitor_storagecpums_iowait_sum + monitor_storagecpums_irq_sum + monitor_storagecpums_softirq_sum) + 100.0*(26.0/38.0)*(monitor_computecpums_user_sum + monitor_computecpums_nice_sum + monitor_computecpums_system_sum + monitor_computecpums_irq_sum + monitor_computecpums_softirq_sum)/(monitor_computecpums_user_sum + monitor_computecpums_nice_sum + monitor_computecpums_system_sum + monitor_computecpums_idle_sum + monitor_computecpums_iowait_sum + monitor_computecpums_irq_sum + monitor_computecpums_softirq_sum))) +
  scale_x_log10(breaks = log_breaks(n=10), label = scales::label_comma(accuracy = 0.1)) +
  scale_y_continuous(breaks = breaks_pretty(n=10), label = scales::label_comma(accuracy = 1)) +
  labs(title = "CPU load", color = "% NDP", shape = "% NDP") +
  xlab("Throughput [requests/second]") + ylab("Cluster CPU utilization (%)")

pdf(paste0(paper_plot_path, "cpu_load.pdf"), width=paper_plot_w, height=paper_plot_h, useDingbats = FALSE, family = paper_font, pointsize = paper_pointsize)
plot(gplt)
dev.off()
gplt
```

### Cluster-total System+User MS / Total MS / Total requests
```{r total_utilization_req}
gplt <- ggplot(t_data %>% filter(rps_offset < 0.05),
    aes(x = avg_rps_avg_rps, group = ndp_factor, color = ndp_factor)) +
  # coord_cartesian(ylim = c(0, 100)) +
  paper_disc_scale + paper_fill_scale + paper_shape_scale + paper_theme +
  geom_line(aes(y = (100.0*(12.0/38.0)*(monitor_storagecpums_user_sum + monitor_storagecpums_nice_sum + monitor_storagecpums_system_sum + monitor_storagecpums_irq_sum + monitor_storagecpums_softirq_sum)/(monitor_storagecpums_user_sum + monitor_storagecpums_nice_sum + monitor_storagecpums_system_sum + monitor_storagecpums_idle_sum + monitor_storagecpums_iowait_sum + monitor_storagecpums_irq_sum + monitor_storagecpums_softirq_sum) + 100.0*(26.0/38.0)*(monitor_computecpums_user_sum + monitor_computecpums_nice_sum + monitor_computecpums_system_sum + monitor_computecpums_irq_sum + monitor_computecpums_softirq_sum)/(monitor_computecpums_user_sum + monitor_computecpums_nice_sum + monitor_computecpums_system_sum + monitor_computecpums_idle_sum + monitor_computecpums_iowait_sum + monitor_computecpums_irq_sum + monitor_computecpums_softirq_sum)) / results_count)) +
  scale_x_log10(breaks = log_breaks(n=10), label = scales::label_comma(accuracy = 0.1)) +
  scale_y_continuous(breaks = breaks_pretty(n=10), label = scales::label_comma()) +
  labs(title = "CPU load", color = "% NDP", shape = "% NDP") +
  xlab("Throughput [requests/second]") + ylab("Cluster CPU utilization per request (%/req)")

pdf(paste0(paper_plot_path, "cpu_load_per_req.pdf"), width=paper_plot_w, height=paper_plot_h, useDingbats = FALSE, family = paper_font, pointsize = paper_pointsize)
plot(gplt)
dev.off()
gplt
```

### Kernel average RUNNING threads
```{r plot_cpu_load}
ggplot(t_data) +
  paper_disc_scale + paper_fill_scale + paper_shape_scale + paper_theme +
  geom_line(stat = 'identity', aes(linetype="Compute",x = avg_rps_avg_rps, y = monitor_computeprocs_running_avg, group = ndp_factor, color = ndp_factor)) +
  geom_line(stat = 'identity', aes(linetype="Storage",x = avg_rps_avg_rps, y = monitor_storageprocs_running_avg, group = ndp_factor, color = ndp_factor)) +
  scale_x_continuous(trans = 'identity', breaks = breaks_pretty(n=20), label = scales::label_comma(accuracy = 1)) +
  scale_y_continuous(trans = 'identity', breaks = breaks_pretty(n=12)) +
  labs(title = "Average RUNNING threads", color = "% NDP", shape = "% NDP", linetype = "Node") +
  xlab("Req/s") + ylab("count")
```

### Faasm average started tasks
```{r plot_faasm_load}
ggplot(t_data) +
  paper_disc_scale + paper_fill_scale + paper_shape_scale + paper_theme +
  geom_line(stat = 'identity', aes(linetype="Compute", x = avg_rps_avg_rps, y = monitor_computefaasm_started_avg, group = ndp_factor, color = ndp_factor)) +
  geom_line(stat = 'identity', aes(linetype="Storage", x = avg_rps_avg_rps, y = monitor_storagefaasm_started_avg, group = ndp_factor, color = ndp_factor)) +
  scale_x_continuous(trans = 'identity', breaks = breaks_pretty(n=20), label = scales::label_comma(accuracy = 1)) +
  scale_y_continuous(trans = 'identity', breaks = breaks_pretty(n=12)) +
  labs(title = "Average started faasm tasks", color = "% NDP", shape = "% NDP", linetype = "Node") +
  xlab("Req/s") + ylab("count")
```

### Faasm average queued-waiting tasks
```{r plot_faasm_load2}
ggplot(t_data) +
  paper_disc_scale + paper_fill_scale + paper_shape_scale + paper_theme +
  geom_line(stat = 'identity', aes(linetype="Compute", x = avg_rps_avg_rps, y = monitor_computefaasm_waiting_queued_avg, group = ndp_factor, color = ndp_factor)) +
  geom_line(stat = 'identity', aes(linetype="Storage", x = avg_rps_avg_rps, y = monitor_storagefaasm_waiting_queued_avg, group = ndp_factor, color = ndp_factor)) +
  scale_x_continuous(trans = 'identity', breaks = breaks_pretty(n=20), label = scales::label_comma(accuracy = 1)) +
  scale_y_continuous(trans = 'identity', breaks = breaks_pretty(n=12)) +
  labs(title = "Average queued-waiting faasm tasks", color = "% NDP", shape = "% NDP", linetype = "Node") +
  xlab("Req/s") + ylab("count")
```

### Context-switches per second
```{r plot_cpu_cswitches}
ggplot(t_data) +
  paper_disc_scale + paper_fill_scale + paper_shape_scale + paper_theme +
  geom_line(stat = 'identity', aes(x = avg_rps_avg_rps, y = monitor_computecswitches_sum / (opts_req_time), group = ndp_factor, color = ndp_factor, linetype = 'Compute')) +
  geom_line(stat = 'identity', aes(x = avg_rps_avg_rps, y = monitor_storagecswitches_sum / (opts_req_time), group = ndp_factor, color = ndp_factor, linetype = 'Storage')) +
  scale_x_continuous(trans = 'identity', breaks = breaks_pretty(n=20), label = scales::label_comma(accuracy = 1)) +
  scale_y_continuous(trans = 'identity', breaks = breaks_pretty(n=12)) +
  labs(title = "Average context switches per second", color = "% NDP", shape = "% NDP", linetype = "Node") +
  xlab("Req/s") + ylab("count/req")
```

### Context-switches per request
```{r plot_cpu_cswitches_req}
ggplot(t_data) +
  paper_disc_scale + paper_fill_scale + paper_shape_scale + paper_theme +
  geom_line(stat = 'identity', aes(x = avg_rps_avg_rps, y = monitor_computecswitches_sum / (total_requests), group = ndp_factor, color = ndp_factor, linetype = 'Compute')) +
  geom_line(stat = 'identity', aes(x = avg_rps_avg_rps, y = monitor_storagecswitches_sum / (total_requests), group = ndp_factor, color = ndp_factor, linetype = 'Storage')) +
  scale_x_continuous(trans = 'log', breaks = log_breaks(n=20), label = scales::label_comma(accuracy = 1)) +
  scale_y_continuous(trans = 'identity') +
  labs(title = "Average context switches per request", color = "% NDP", shape = "% NDP", linetype = "Node") +
  xlab("Req/s") + ylab("count/request")
```

### Linux load 1m-exp rolling average
```{r plot_load_req}
ggplot(t_data) +
  paper_disc_scale + paper_fill_scale + paper_shape_scale + paper_theme +
  geom_line(stat = 'identity', aes(x = avg_rps_avg_rps, y = monitor_computeload_avg1_avg, group = ndp_factor, color = ndp_factor, linetype = 'Compute')) +
  geom_line(stat = 'identity', aes(x = avg_rps_avg_rps, y = monitor_storageload_avg1_avg, group = ndp_factor, color = ndp_factor, linetype = 'Storage')) +
  scale_x_continuous(trans = 'log', breaks = log_breaks(n=20), label = scales::label_comma(accuracy = 1)) +
  scale_y_continuous(trans = 'identity', breaks = breaks_pretty(n = 10)) +
  labs(title = "Load", color = "% NDP", shape = "% NDP", linetype = "Node") +
  xlab("Req/s") + ylab("1m average load")
```

### Per-node User+system CPU ms per request
```{r plot_cpu_ms_pr}
ggplot(t_data) +
  paper_disc_scale + paper_fill_scale + paper_shape_scale + paper_theme +
  geom_line(stat = 'identity', aes(x = avg_rps_avg_rps, y = (monitor_computecpums_user_sum + monitor_computecpums_system_sum + monitor_computecpums_nice_sum) / (results_count), group = ndp_factor, color = ndp_factor, linetype = 'Compute')) +
  geom_line(stat = 'identity', aes(x = avg_rps_avg_rps, y = (monitor_storagecpums_user_sum + monitor_storagecpums_system_sum + monitor_storagecpums_nice_sum) / (results_count), group = ndp_factor, color = ndp_factor, linetype = 'Storage')) +
  scale_x_continuous(trans = 'log', breaks = log_breaks(n=20), label = scales::label_comma(accuracy = 1)) +
  scale_y_continuous(trans = 'identity', breaks = pretty_breaks(n=20)) +
  labs(title = "Average CPU ms per request (user+system)", color = "% NDP", shape = "% NDP", linetype = "Node") +
  xlab("Req/s") + ylab("count")
```

### Cluster-total User+system CPU ms per request
```{r plot_cpu_ms_pr_ct}
ggplot(t_data) +
  paper_disc_scale + paper_fill_scale + paper_shape_scale + paper_theme +
  geom_line(stat = 'identity', aes(x = avg_rps_avg_rps, y = (monitor_computecpums_user_sum + monitor_computecpums_system_sum + monitor_computecpums_nice_sum + monitor_storagecpums_user_sum + monitor_storagecpums_system_sum + monitor_storagecpums_nice_sum) / (results_count), group = ndp_factor, color = ndp_factor)) +
  scale_x_continuous(trans = 'log', breaks = log_breaks(n=20), label = scales::label_comma(accuracy = 1)) +
  scale_y_continuous(trans = 'identity', breaks = breaks_pretty(n=10)) +
  labs(title = "Average CPU ms per request (user+system)", color = "% NDP", shape = "% NDP") +
  xlab("Req/s") + ylab("count")
```

## Memory statistics

### Average active memory
```{r plot_mem_active_c}
cmembase <- as.double(min(t_data$monitor_computemem_active_min))
ggplot(t_data) +
  paper_disc_scale + paper_fill_scale + paper_shape_scale + paper_theme +
  geom_line(stat = 'identity', aes(x = avg_rps_avg_rps, y = monitor_computemem_active_avg - !!cmembase, group = ndp_factor, color = ndp_factor, linetype = 'Compute')) +
  scale_x_continuous(trans = 'log', breaks = log_breaks(n=20), label = scales::label_comma(accuracy = 1)) +
  scale_y_continuous(trans = 'identity', breaks = breaks_pretty(n=20), label = scales::label_comma(accuracy = 1)) +
  labs(title = "Average Active memory per request over baseline") +
  xlab("Req/s") + ylab("bytes")
```

```{r plot_mem_active_s}
smembase <- as.double(min(t_data$monitor_storagemem_active_min))
ggplot(t_data) +
  paper_disc_scale + paper_fill_scale + paper_shape_scale + paper_theme +
  geom_line(stat = 'identity', aes(x = avg_rps_avg_rps, y = monitor_storagemem_active_avg - !!smembase, group = ndp_factor, color = ndp_factor, linetype = 'Storage')) +
  scale_x_continuous(trans = 'log', breaks = log_breaks(n=20), label = scales::label_comma(accuracy = 1)) +
  scale_y_continuous(trans = 'identity', breaks = breaks_pretty(n=20), label = scales::label_comma(accuracy = 1)) +
  labs(title = "Average Active memory per request over baseline") +
  xlab("Req/s") + ylab("bytes")
```

## Network

### Per-node TX bytes per request
```{r plot_net_tx_bytes}
ggplot(t_data) +
  paper_disc_scale + paper_fill_scale + paper_shape_scale + paper_theme +
  geom_line(stat = 'identity', aes(x = avg_rps_avg_rps, y = monitor_computenet_tx_bytes_sum / total_requests, group = ndp_factor, color = ndp_factor, linetype = 'Compute')) +
  geom_line(stat = 'identity', aes(x = avg_rps_avg_rps, y = monitor_storagenet_tx_bytes_sum / total_requests, group = ndp_factor, color = ndp_factor, linetype = 'Storage')) +
  scale_x_continuous(trans = 'log', breaks = log_breaks(n=20), label = scales::label_comma(accuracy = 1)) +
  scale_y_continuous(trans = 'log', breaks = log_breaks(n=20), label = scales::label_comma(accuracy = 1)) +
  labs(title = "Total bytes per request sent from node over network") +
  xlab("Req/s") + ylab("bytes/request")
```

### Cluster TX per request
```{r plot_net_tx_sum_bytes}
ggplot(t_data) +
  paper_disc_scale + paper_fill_scale + paper_shape_scale + paper_theme +
  geom_line(stat = 'identity', aes(x = avg_rps_avg_rps, y = (monitor_computenet_tx_bytes_sum + monitor_storagenet_tx_bytes_sum) / total_requests, group = ndp_factor, color = ndp_factor)) +
  scale_x_continuous(trans = 'log', breaks = log_breaks(n=20), label = scales::label_comma(accuracy = 1), expand = c(0.01, 0.01)) +
  scale_y_continuous(trans = 'identity', expand = c(0.1,0), limits = c(0, NA), label = scales::label_comma(accuracy = 1)) +
  labs(title = "Total bytes per request sent over network") +
  xlab("Req/s") + ylab("bytes/request")
```

### Cluster TX per second
```{r plot_net_tx_sum_bytes_per_sec}
ggplot(t_data) +
  paper_disc_scale + paper_fill_scale + paper_shape_scale + paper_theme +
  geom_line(stat = 'identity', aes(x = avg_rps_avg_rps, y = (monitor_computenet_tx_bytes_sum + monitor_storagenet_tx_bytes_sum) / (opts_req_time), group = ndp_factor, color = ndp_factor)) +
  scale_x_continuous(trans = 'identity', breaks = breaks_pretty(n=20), label = scales::label_comma(accuracy = 1), expand = c(0.01, 0.01)) +
  scale_y_continuous(trans = 'identity', expand = c(0.1,0), limits = c(0, NA), label = scales::label_comma(accuracy = 1)) +
  labs(title = "Total bytes per second sent over network") +
  xlab("Req/s") + ylab("bytes/second")
```

## Cross-verification

### RPS/RPS cross-verification
```{r plot_xverify_rps}
ggplot(t_data) +
  paper_disc_scale + paper_fill_scale + paper_shape_scale + paper_theme +
  geom_point(stat = 'identity', aes(x = opts_req_rps, y = avg_rps_avg_rps, group = ndp_factor, color = ndp_factor, shape=ndp_factor)) +
  scale_x_continuous(trans = 'identity', label = scales::label_comma(accuracy = 1), expand = c(0.01, 0.01)) +
  scale_y_continuous(trans = 'identity', expand = c(0.1,0), limits = c(0, NA), label = scales::label_comma(accuracy = 1)) +
  labs(title = "Xverify RPS/RPS") +
  ylab("Real Req/s") + xlab("Requested Req/s")
```


### NDP-NDP cross-verification
```{r plot_xverify_ndp}
ggplot(t_data) +
  paper_disc_scale + paper_fill_scale + paper_shape_scale + paper_theme +
  geom_point(stat = 'identity', aes(x = opts_actual_ndp, y = ndp_factor, group = ndp_factor, color = ndp_factor)) +
  labs(title = "Xverify NDP") +
  xlab("Real NDP") + ylab("Requested NDP")
```
