---
title: "CPU and DPU memory performance analysis"
author: "Jakub Szewczyk"
date: "10/12/2020"
output:
  pdf_document:
    toc: yes
  html_document:
    toc: yes
---

```{r setup, include=FALSE}
library(tidyverse)
library(tidyjson)
knitr::opts_chunk$set(echo = FALSE)
```

```{r read_json, include=FALSE, cache=TRUE, cache.extra = file.info("combined.json")}
raw_json <- tidyjson::read_json("combined.json")
bench_meta <-
  raw_json %>% enter_object(context) %>% spread_all %>% transpose %>% simplify_all %>% `[[`(1)
bench_raw <-
  raw_json %>% enter_object(benchmarks) %>% gather_array %>% spread_all
```

```{r tidy_bench}
# Benchmark names:
# BM_cpu_memcopy/4
# BM_cpu_memread_linear/4
# BM_cpu_memread_listwalk/134217728
# DpuBenchFixture/BM_dpu_copy_between_cpu_dpu/dwords:2/dpus:8/broadcast:0/to_dpu:0/mram:1/real_time
# DpuBenchFixture/BM_dpu_copy_within/dwords:1024/dpus:8/dpu_reps:64/dpu_threads:12/mram:1/real_time

t_cpu_memcopy <- bench_raw %>%
  filter(str_detect(name, "^BM_cpu_memcopy/")) %>%
  select(name, iterations, cpu_time, bytes_per_second, memused) %>%
  extract(
    name,
    into = c("dwords"),
    regex = "^BM_cpu_memcopy/([0-9]+)",
    remove = TRUE,
    convert = TRUE
  )

t_cpu_memread_linear <- bench_raw %>%
  filter(str_detect(name, "^BM_cpu_memread_linear/")) %>%
  select(name, iterations, cpu_time, bytes_per_second, memused) %>%
  extract(
    name,
    into = c("dwords"),
    regex = "^BM_cpu_memread_linear/([0-9]+)",
    remove = TRUE,
    convert = TRUE
  )

t_cpu_memread_listwalk <- bench_raw %>%
  filter(str_detect(name, "^BM_cpu_memread_listwalk/")) %>%
  select(name, iterations, cpu_time, bytes_per_second, memused) %>%
  extract(
    name,
    into = c("dwords"),
    regex = "^BM_cpu_memread_listwalk/([0-9]+)",
    remove = TRUE,
    convert = TRUE
  )

t_cpu_dpu_copy <- bench_raw %>%
  filter(str_detect(name, "^DpuBenchFixture/BM_dpu_copy_between_cpu_dpu/")) %>%
  select(name, iterations, cpu_time, real_time, bytes_per_second, memused, dpu_ranks) %>%
  extract(
    name,
    into = c("dwords", "dpus", "broadcast", "to_dpu", "mram"),
    regex = "^DpuBenchFixture/BM_dpu_copy_between_cpu_dpu/dwords:([0-9]+)/dpus:([0-9]+)/broadcast:([01])/to_dpu:([01])/mram:([01])/real_time",
    remove = TRUE,
    convert = TRUE
  ) %>%
  unite(direction, broadcast, to_dpu, sep=";") %>%
  mutate(
    direction = factor(direction, levels=c("0;0", "0;1", "1;1"), labels=c("Read from all", "Write N->N", "Broadcast 1->N")),
    mram = factor(mram, levels=c("0", "1"), labels=c("WRAM", "MRAM")),
    dpu_ranks = factor(dpu_ranks),
    dpus = factor(dpus)
  )

t_dpu_copy <- bench_raw %>%
  filter(str_detect(name, "^DpuBenchFixture/BM_dpu_copy_within/")) %>%
  select(name, iterations, cpu_time, real_time, bytes_per_second, dpu_ranks) %>%
  extract(
    name,
    into = c("dwords", "dpus", "dpu_reps", "dpu_threads", "mram"),
    regex = "^DpuBenchFixture/BM_dpu_copy_within/dwords:([0-9]+)/dpus:([0-9]+)/dpu_reps:([0-9]+)/dpu_threads:([0-9]+)/mram:([01])/real_time",
    remove = TRUE,
    convert = TRUE
  ) %>%
  mutate(
    memused = 4*dwords,
    dpu_batch_size = dpu_reps*4*dwords,
    mram = factor(mram, levels=c("0", "1"), labels=c("WRAM", "MRAM")),
    dpu_ranks = factor(dpu_ranks),
    dpus = factor(dpus),
    dpu_reps = factor(dpu_reps)
  )

```

## Benchmark metadata

The benchmarks were run on a `r bench_meta$num_cpus`-core `r bench_meta$mhz_per_cpu` MHz CPU.

## Reference point: CPU memory bandwidth

For reference here are the cache sizes for the CPU:
```{r cpu_cache_info}
bench_meta %>% enter_object("caches") %>% gather_array() %>% spread_all %>%
  as_tibble() %>%
  select(type, level, size, num_sharing) %>%
  mutate(size = scales::label_bytes(units = "auto_binary")(size)) %>%
  knitr::kable(col.names = c("Type", "Level", "Size", "Cores sharing"))
```

```{r plot_cpu_memcopy}
ggplot(t_cpu_memcopy) +
  geom_point(mapping = aes(x = dwords * 4.0, y = bytes_per_second / (1024 ^ 3))) +
  scale_x_continuous(trans = 'log2', n.breaks = 8, labels = scales::label_bytes(units="auto_binary")) +
  labs(title = "Speed of a simple memory copy showing cache size influence") +
  xlab("Bytes copied") + ylab("GB/s")
```

```{r plot_cpu_linwalk}
ggplot(t_cpu_memread_linear) +
  geom_point(mapping = aes(x = dwords * 4.0, y = bytes_per_second / (1024 ^ 3))) +
  scale_x_continuous(trans = 'log2', n.breaks = 8, labels = scales::label_bytes(units="auto_binary")) +
  labs(title = "Memory read (linear) speed") +
  xlab("Bytes read") + ylab("GB/s")
```

```{r plot_cpu_listwalk}
ggplot(t_cpu_memread_listwalk) +
  geom_point(mapping = aes(x = dwords * 4.0, y = bytes_per_second / (1024 ^ 3))) +
  scale_x_continuous(trans = 'log2', n.breaks = 8, labels = scales::label_bytes(units="auto_binary")) +
  labs(title = "Memory read (listwalk) speed") +
  xlab("Bytes read") + ylab("GB/s")
```

## Transfers between CPU and DPU

### WRAM (static local RAM on the DPU)

```{r plot_cpu_dpu_wram}
ggplot(t_cpu_dpu_copy %>% filter(mram=="WRAM"),
       aes(x = memused, y = bytes_per_second / (1024 ^ 2), shape=direction, color=dpus)) +
  geom_point(size = 2) +
  geom_smooth(se=FALSE, size=0.25, formula = y ~ log2(x), method = "loess") +
  scale_x_continuous(trans = 'log2', n.breaks = 8, labels = scales::label_bytes(units="auto_binary")) +
  scale_y_continuous(trans = 'log2', n.breaks = 8) +
  scale_shape_manual(values = c(0, 3, 4)) +
  labs(title = "CPU<->DPU WRAM copy speed") +
  xlab("Bytes copied") + ylab("MB/s")
```

```{r plot_cpu_dpu_wram_latency}

ggplot(t_cpu_dpu_copy %>% filter(mram=="WRAM", memused<=512),
       aes(x = memused, y = real_time * 1e-3, shape=direction, color=dpus)) +
  geom_point(size=2.5) +
  scale_x_continuous(trans = 'log2', n.breaks = 8) +
  scale_y_continuous(trans = 'log10', n.breaks = 8) +
  scale_shape_manual(values = c(0, 3, 4)) +
  labs(title = "CPU<->DPU WRAM copy latency") +
  xlab("Bytes copied per DPU") + ylab("Microsecond latency") +
  facet_wrap(vars(direction))
```

### MRAM (64MB DRAM block next to the DPU)

```{r plot_cpu_dpu_mram, fig.height = 8}
ggplot(t_cpu_dpu_copy %>% filter(mram=="MRAM"),
       aes(x = memused, y = bytes_per_second / (1024 ^ 2), shape=direction, color=dpus)) +
  geom_point(size = 2) +
  geom_smooth(se=FALSE, size=0.25, formula = y ~ log2(x), method = "loess") +
  scale_x_continuous(trans = 'log2', n.breaks = 8, labels = scales::label_bytes(units="auto_binary")) +
  scale_y_continuous(trans = 'log2', n.breaks = 8) +
  scale_shape_manual(values = c(0, 3, 4)) +
  labs(title = "CPU<->DPU MRAM copy speed") +
  xlab("Bytes copied") + ylab("MiB per second") +
  facet_grid(rows=vars(direction))
```

```{r plot_cpu_dpu_mram_latency}

ggplot(t_cpu_dpu_copy %>% filter(mram=="MRAM", memused<=512),
       aes(x = memused, y = real_time * 1e-3, shape=direction, color=dpus)) +
  geom_point(size=2.5) +
  scale_x_continuous(trans = 'log2', n.breaks = 8) +
  scale_y_continuous(trans = 'log10', n.breaks = 8) +
  scale_shape_manual(values = c(0, 3, 4)) +
  labs(title = "CPU<->DPU MRAM copy latency") +
  xlab("Bytes copied per DPU") + ylab("Microsecond latency") +
  facet_wrap(vars(direction))
```

## In-DPU copy performance (bandwidth)

### WRAM

```{r plot_dpu_wram}

ggplot(t_dpu_copy %>% filter(mram=="WRAM"),
       aes(x = dpu_batch_size, y = bytes_per_second / 1024^2, color=dpus, shape=dpu_reps)) +
  geom_point(size=2.5) +
  scale_x_continuous(trans = 'log2', n.breaks = 8, labels = scales::label_bytes(units="auto_binary")) +
  scale_y_continuous(trans = 'log10', n.breaks = 8) +
  scale_shape_manual(values = c(0, 3, 4)) +
  labs(title = "DPU WRAM<->WRAM copy bandwidth (including CPU dispatch overhead)") +
  xlab("Bytes copied per DPU") + ylab("MiB per second")
```

```{r plot_dpu_wram_latency}

ggplot(t_dpu_copy %>% filter(mram=="WRAM"),
       aes(x = dpu_batch_size, y = real_time * 1e-3, color=dpus, shape=dpu_reps)) +
  geom_point(size=2.5) +
  scale_x_continuous(trans = 'log2', n.breaks = 8, labels = scales::label_bytes(units="auto_binary")) +
  scale_y_continuous(trans = 'log10', n.breaks = 8) +
  scale_shape_manual(values = c(0, 3, 4)) +
  labs(title = "DPU WRAM<->WRAM copy latency (including CPU dispatch overhead)") +
  xlab("Bytes copied per DPU") + ylab("Microsecond latency")
```

### MRAM

64-byte window was used as a block size for DMA transfers between the MRAM and WRAM. (TODO: A couple more of window sizes)

```{r plot_dpu_mram}

ggplot(t_dpu_copy %>% filter(mram=="MRAM"),
       aes(x = dpu_batch_size, y = bytes_per_second / 1024^2, color=dpus, shape=dpu_reps)) +
  geom_point(size=2.5) +
  scale_x_continuous(trans = 'log2', n.breaks = 8, labels = scales::label_bytes(units="auto_binary")) +
  scale_y_continuous(trans = 'log10', n.breaks = 8) +
  scale_shape_manual(values = c(0, 3, 4)) +
  labs(title = "DPU MRAM<WRAM>MRAM copy bandwidth (including CPU dispatch overhead)") +
  xlab("Bytes copied per DPU") + ylab("MiB per second per DPU")
```

```{r plot_dpu_mram_total}

ggplot(t_dpu_copy %>% filter(mram=="MRAM"),
       aes(x = dpu_batch_size, y = bytes_per_second * as.numeric(dpus), color=dpus, shape=dpu_reps)) +
  geom_point(size=2.5) +
  scale_x_continuous(trans = 'log2', n.breaks = 8, labels = scales::label_bytes(units="auto_binary")) +
  scale_y_continuous(trans = 'log10', n.breaks = 8, labels = scales::label_bytes(units="auto_binary")) +
  scale_shape_manual(values = c(0, 3, 4)) +
  labs(title = "DPU MRAM<WRAM>MRAM copy bandwidth total (including CPU dispatch)") +
  xlab("Bytes copied per DPU") + ylab("bytes per second total for all DPUs")
```

```{r plot_dpu_mram_lat}

ggplot(t_dpu_copy %>% filter(mram=="MRAM"),
       aes(x = dpu_batch_size, y = real_time * 1e-3, color=dpus, shape=dpu_reps)) +
  geom_point(size=2.5) +
  scale_x_continuous(trans = 'log2', n.breaks = 8, labels = scales::label_bytes(units="auto_binary")) +
  scale_y_continuous(trans = 'log10', n.breaks = 8, labels = scales::label_number()) +
  scale_shape_manual(values = c(0, 3, 4)) +
  labs(title = "DPU MRAM<WRAM>MRAM copy latency (including CPU dispatch overhead)") +
  xlab("Bytes copied per DPU") + ylab("Microsecond latency")
```
